The \dealii Library, Version 9.7

### 2025-08-20 9.7/paper.tex
Address minor spacing issues.

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release: Around 125 of the more than 1500 (non-merge)
commits that went into this release touched the tutorial.
% data generated using these commands:
% - tutorial: git log --since 2024/08/11 --until 2025/07/19 --no-merges examples | grep commit | wc -l
% - total:    git log --since 2024/08/11 --until 2025/07/19 --no-merges | grep commit | wc -l
In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \step{93}
    demonstrates how one can implement problems in which some of the
    variables to be solved for are not degrees of freedom of a finite
    element field (i.e., they are ``non-local'' degrees of freedom, because
    they have no associated node functional that is tied to a cell or
    a patch of cells). Specifically, the program solves an
    optimization problem in which some of the variables are scalars
    that multiply certain source terms.
    \step{93} was written by Sam Scheuerman.
  \item
    \step{95} extends \step{85} and illustrates the use of matrix-free methods to solve
    problems with embedded boundaries using the CutFEM method~\cite{bergbauer2025high}. 
    It shows the interplay between the matrix-free infrastructure for standard quadrature rules 
    (\texttt{FEEvaluation} / \texttt{MatrixFree}) and the infrastructure for unstructured
     quadrature (\texttt{FEPointEvaluation} / \texttt{NonMatching::MappingInfo}) while using explicit 
     \texttt{SIMD} vectorization. The tutorial implements both continuous and discontinuous Galerkin 
     methods in 2D and 3D.
    \step{95} was written by Maximilian Bergbauer, with help by Martin Kronbichler and Peter Munch.
  \item
    \step{97}
    is a program that solves a curl-curl problem from electromagnetics
    -- more specifically, from magnetostatics. The program shows a
    formulation in which two curl-curl problems are solved
    consecutively to model the magnetic field that results from the
    current in an electrically conducting coil.
    \step{97} was written by Siarhei Uzunbajakau.
\end{itemize}

>>>>

Many of the \dealii tutorial programs were revised in a variety of ways
as part of this release: Around 125 of the more than 1500 (non-merge)
commits that went into this release touched the tutorial.
% data generated using these commands:
% - tutorial: git log --since 2024/08/11 --until 2025/07/19 --no-merges examples | grep commit | wc -l
% - total:    git log --since 2024/08/11 --until 2025/07/19 --no-merges | grep commit | wc -l
In addition, there are a number of new tutorial
programs:
\begin{itemize}
  \item
    \step{93}
    demonstrates how one can implement problems in which some of the
    variables to be solved for are not degrees of freedom of a finite
    element field (i.e., they are ``non-local'' degrees of freedom, because
    they have no associated node functional that is tied to a cell or
    a patch of cells). Specifically, the program solves an
    optimization problem in which some of the variables are scalars
    that multiply certain source terms.
    \step{93} was written by Sam Scheuerman.
  \item
    \step{95} extends \step{85} and illustrates the use of matrix-free methods to solve
    problems with embedded boundaries using the CutFEM method~\cite{bergbauer2025high}. 
    It shows the interplay between the matrix-free infrastructure for standard quadrature rules 
    (\texttt{FEEvaluation}/\texttt{MatrixFree}) and the infrastructure for unstructured
     quadrature (\texttt{FEPointEvaluation}/\texttt{NonMatching::MappingInfo}) while using explicit 
     \texttt{SIMD} vectorization. The tutorial implements both continuous and discontinuous Galerkin 
     methods in 2D and 3D.
    \step{95} was written by Maximilian Bergbauer, with help by Martin Kronbichler and Peter Munch.
  \item
    \step{97}
    is a program that solves a curl-curl problem from electromagnetics
    -- more specifically, from magnetostatics. The program shows a
    formulation in which two curl-curl problems are solved
    consecutively to model the magnetic field that results from the
    current in an electrically conducting coil.
    \step{97} was written by Siarhei Uzunbajakau.
\end{itemize}
